Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex
Added need lemma from bijective lens paper

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{letltxmacro}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}
\usepackage{bbm}

@@

Similar to the previous case.
\end{enumerate}
\end{proof}

\begin{theorem*}
  $\ProbabilityOf{\Regex}{\String} = \ProbabilityOf{\ToDNFRegex
    \Regex}{\String}$ and $\LanguageOf{\Regex} =
  \LanguageOf{\ToDNFRegexOf{\Regex}}$
\end{theorem*}
\begin{proof}
By \sam{COPY PASTE PROOF FROM BIJECTIVE LENS PAPER} $\LanguageOf{\Regex} =
  \LanguageOf{\ToDNFRegexOf{\Regex}}$, so we will prove the result $\ProbabilityOf{\Regex}{\String} = \ProbabilityOf{\ToDNFRegex
    \Regex}{\String}$.
\begin{enumerate}
\item
$(S = s)$

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[capitalise]{cleveref}
\usepackage{amsmath}
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{letltxmacro}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}
\usepackage{bbm}

@@

Similar to the previous case.
\end{enumerate}
\end{proof}
\begin{mylemma}[Equivalence of \ConcatSequence{} and \Concat{}]
  If $\LanguageOf{\Regex}=\LanguageOf{\Sequence}$,
  and $\LanguageOf{\RegexAlt}=\LanguageOf{\SequenceAlt}$,
  then $\LanguageOf{\RegexConcat{\Regex}{\RegexAlt}}=\LanguageOf{\ConcatSequenceOf{\Sequence}{\SequenceAlt}}$.
\end{mylemma}
\begin{proof}
  Let $\Sequence=\SequenceOf{\String_0\SeqSep\Atom_1\SeqSep\ldots
    \SeqSep\Atom_n\SeqSep\String_n}$, and
  let $\SequenceAlt=[\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots
  \SeqSep\AtomAlt_m\SeqSep\StringAlt_m]$. Then
  \begin{align*}  
    \LanguageOf{\ConcatSequenceOf{\Sequence}{\SequenceAlt}} & = 
                                                              \LanguageOf{\SequenceOf{\String_0\SeqSep\Atom_1\SeqSep\ldots
                                                              \SeqSep\Atom_n\SeqSep\String_n\Concat\StringAlt_0\SeqSep{}
                                                              \AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\StringAlt_m}} \\
                                                            & = 
                                                              \{\String_0\Concat\String_1'\Concat\ldots\Concat\String_n'\Concat\String_n
                                                              \Concat\StringAlt_0\Concat\StringAlt_1'\Concat\ldots
                                                              \Concat\StringAlt_m'\Concat\StringAlt_m\SuchThat{} \String_i'\in\LanguageOf{\Atom_i} \BooleanAnd{}
                                                              \StringAlt_i'\in\LanguageOf{\AtomAlt_i}\}\\
                                                            & = 
                                                              \{\String\Concat\StringAlt{} \SuchThat{} \String\in\LanguageOf{\Sequence}
                                                              \BooleanAnd{} \StringAlt\in\LanguageOf{\SequenceAlt}\}\\
                                                            & =
                                                              \{\String\Concat\StringAlt{} \SuchThat{} \String\in\LanguageOf{\Regex}
                                                              \BooleanAnd{} \StringAlt\in\LanguageOf{\RegexAlt}\}\\
                                                            & =
                                                              \LanguageOf{\RegexConcat{\Regex}{\RegexAlt}}
\end{align*}
\end{proof}

\begin{mylemma}[Equivalence of \ConcatDNF{} and \Concat{}]
  \label{lem:cdnfeq}
  If $\LanguageOf{\Regex}=\LanguageOf{\DNFRegex}$,
  and $\LanguageOf{\RegexAlt}=\LanguageOf{\DNFRegexAlt}$,
  then $\LanguageOf{\RegexConcat{\Regex}{\RegexAlt}}=
  \LanguageOf{\ConcatDNFOf{\DNFRegex}{\DNFRegexAlt}}$.
\end{mylemma}
\begin{proof}
  Let $\DNFRegex=\DNFOf{\Sequence_0\DNFSep\ldots\DNFSep\Sequence_n}$, and
  let $\DNFRegexAlt=\DNFOf{\SequenceAlt_0\DNFSep\ldots\DNFSep\SequenceAlt_m}$
  \begin{align*}
    \LanguageOf{\ConcatDNFOf{\DNFRegex}{\DNFRegexAlt}} & = 
                                                         \LanguageOf{\DNFOf{\ConcatSequenceOf{\Sequence_i}{\SequenceAlt_j}
                                                         \text{ for $i\in\RangeIncInc{1}{n}$, $j\in\RangeIncInc{1}{m}$}}} \\
                                                       & = 
                                                         \{\String\SuchThat \String\in\ConcatSequenceOf{\Sequence_i}{\SequenceAlt_j} \text{ where $i\in\RangeIncInc{1}{n}$, $j\in\RangeIncInc{1}{m}$}\}\\
                                                       & = 
                                                         \{\String\Concat\StringAlt{} \SuchThat{} \String\in\LanguageOf{\Sequence_i}
                                                         \BooleanAnd{} \StringAlt\in\LanguageOf{\SequenceAlt_j}\} \text{ where $i\in\RangeIncInc{1}{n}$, $j\in\RangeIncInc{1}{m}$}\}\\
                                                       & =
                                                         \{\String\Concat\StringAlt{} \SuchThat{} \String\in\LanguageOf{\DNFRegex}
                                                         \BooleanAnd{} \StringAlt\in\LanguageOf{\DNFRegexAlt}\}\\
                                                       & =
                                                         \{\String\Concat\StringAlt{} \SuchThat{} \String\in\LanguageOf{\Regex}
                                                         \BooleanAnd{} \StringAlt\in\LanguageOf{\RegexAlt}\}\\
                                                       & =
                                                         \LanguageOf{\RegexConcat{\Regex}{\RegexAlt}}
\end{align*}
\end{proof}

\begin{mylemma}[Equivalence of $\Atom$ and $\AtomToDNFOf{\Atom}$]
  \label{lem:atomtodnfeq}
  $\LanguageOf{\Atom} = \LanguageOf{\AtomToDNFOf{\Atom}}$
\end{mylemma}
\begin{proof}
\begin{align*}
  \LanguageOf{\AtomToDNFOf{\Atom}} &=
  \LanguageOf{\DNFOf{\SequenceOf{\EmptyString \SeqSep \Atom \SeqSep \EmptyString}}}\\
  & =
  \SetOf{\String \SuchThat \String \in
    \LanguageOf{\SequenceOf{\EmptyString \SeqSep \Atom \SeqSep \EmptyString}}} \\
  & =
  \SetOf{\EmptyString\Concat\String\Concat\EmptyString \SuchThat \String \in
    \LanguageOf{\Atom}} \\
   & = \SetOf{\String \SuchThat \String \in
    \LanguageOf{\Atom}} \\
    &= \LanguageOf{\Atom}
    \end{align*}
\end{proof}

\begin{mylemma}[Equivalence of \OrDNF{} and \Or{}]
  \label{lem:odnfeq}
  If $\LanguageOf{\Regex}=\LanguageOf{\DNFRegex}$,
  and $\LanguageOf{\RegexAlt}=\LanguageOf{\DNFRegexAlt}$,
  then $\LanguageOf{\RegexOr{\Regex}{\RegexAlt}}=
  \LanguageOf{\OrDNFOf{\DNFRegex}{\DNFRegexAlt}}$.
\end{mylemma}
\begin{proof}
  Let $\DNFRegex=\DNFOf{\Sequence_0\DNFSep\ldots\DNFSep\Sequence_n}$, and
  let $\DNFRegexAlt=\DNFOf{\SequenceAlt_0\DNFSep\ldots\DNFSep\SequenceAlt_m}$

  \begin{align*}
    \mathcal{L}(DS \oplus DT)& = 
                                                     \LanguageOf{\DNFOf{\Sequence_0\DNFSep\ldots\DNFSep\Sequence_n\DNFSep
                                                     \SequenceAlt_1\DNFSep\ldots\DNFSep\SequenceAlt_m}}\\
                                                   & = 
                                                     \{\String\SuchThat{} \String\in\Sequence_i\vee\String\in\SequenceAlt_j \text{ where $i\in\RangeIncInc{1}{n}$, $j\in\RangeIncInc{1}{m}$}\}\\
                                                   & = 
                                                     \{\String{} \SuchThat{} \String\in\LanguageOf{\DNFRegex}
                                                     \BooleanOr{} \String\in\LanguageOf{\DNFRegexAlt}\}\\
                                                   & =
                                                     \{\String \SuchThat{} \String\in\LanguageOf{\Regex}
                                                     \BooleanOr{} \String\in\LanguageOf{\RegexAlt}\}\\
                                                   & =
                                                     \LanguageOf{\RegexOr{\Regex}{\RegexAlt}}
  \end{align*}
\end{proof}

\begin{theorem}\label{ConversionPreservesSemantics}
  For all regular expressions \Regex{},
  $\LanguageOf{\ToDNFRegexOf{\Regex}}=\LanguageOf{\Regex{}}$.
\end{theorem}
\begin{proof}
  By structural induction.

  Let $\Regex=\String$.
  $\LanguageOf{\ToDNFRegex(\String)}=\LanguageOf{\DNFOf{\SequenceOf{\String}}}=
  \{\String\}=\LanguageOf{\String}$

  Let $\Regex=\emptyset$.
  $\LanguageOf{\ToDNFRegex(\emptyset)}=\LanguageOf{\DNFOf{}} =
  \{\} = \LanguageOf{\emptyset}$.

  Let $\Regex=\StarOf{\Regex'}$.
  By induction assumption, $\LanguageOf{\ToDNFRegex(\Regex')}=
  \LanguageOf{\Regex'}$.
  \begin{align*}
    \LanguageOf{\ToDNFRegex(\StarOf{\DNFRegex'})} & =
                                                    \LanguageOf{\DNFOf{\SequenceOf{\StarOf{\ToDNFRegex(\Regex')}}}}\\
                                                  & =
                                                    \{\String\SuchThat\String\in
                                                    \LanguageOf{\SequenceOf{\StarOf{\ToDNFRegex(\Regex')}}}\}\\
                                                  & = 
                                                    \{\String\SuchThat{} \String\in\LanguageOf{\StarOf{\ToDNFRegex(\Regex')}}\}\\
                                                  & =
                                                    \{\String_1\Concat\ldots\Concat\String_n\SuchThat{}
                                                    n\in\Nats \BooleanAnd\String_i\in\LanguageOf{\ToDNFRegex(\Regex')}\}\\
                                                  & =
                                                    \{\String_1\Concat\ldots\Concat\String_n\SuchThat{}
                                                    n\in\Nats\BooleanAnd\String_i\in\LanguageOf{\Regex'}\}\\
                                                  & = \LanguageOf{\StarOf{\Regex'}}
  \end{align*}

  Let $\Regex=\RegexConcat{\Regex_1}{\Regex_2}$.
  By induction assumption,
  $\LanguageOf{\ToDNFRegex(\Regex_1)}=\LanguageOf{\Regex_1}$, and
  $\LanguageOf{\ToDNFRegex(\Regex_2)}=\LanguageOf{\Regex_2}$.
  $\ToDNFRegex(\RegexConcat{\Regex_1}{\Regex_2})=
  \ConcatDNFOf{\ToDNFRegex(\Regex_1)}{\ToDNFRegex(\Regex_2)}$.
  By Lemma~\ref{lem:cdnfeq},
  $\RegexConcat{\Regex_1}{\Regex_2}=
  \ConcatDNFOf{\ToDNFRegex(\Regex_1)}{\ToDNFRegex(\Regex_2)}$.

  Let $\Regex=\RegexOr{\Regex_1}{\Regex_2}$.
  By induction assumption,
  $\LanguageOf{\ToDNFRegex(\Regex_1)}=\LanguageOf{\Regex_1}$, and
  $\LanguageOf{\ToDNFRegex(\Regex_2)}=\LanguageOf{\Regex_2}$.

  $\Downarrow(S \; | \; T) = (\Downarrow S) \oplus (\Downarrow T)$. By Lemma~\ref{lem:odnfeq},
  $\mathcal{L}(S \; | \; T) = \mathcal{L}((\Downarrow S) \oplus (\Downarrow T))$.

\end{proof}
\begin{theorem*}
  $\ProbabilityOf{\Regex}{\String} = \ProbabilityOf{\ToDNFRegex
    \Regex}{\String}$ and $\LanguageOf{\Regex} =
  \LanguageOf{\ToDNFRegexOf{\Regex}}$
\end{theorem*}
\begin{proof}
By \cref{ConversionPreservesSemantics}, $\LanguageOf{\Regex} =
  \LanguageOf{\ToDNFRegexOf{\Regex}}$, so we will prove the result $\ProbabilityOf{\Regex}{\String} = \ProbabilityOf{\ToDNFRegex
    \Regex}{\String}$.
\begin{enumerate}
\item
$(S = s)$
